Turbulence in compact to giant H~II regions

### 2022-12-19 strucfunc_paper.tex
Javier changes 2022-12-19

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
  In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
  We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
  We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
  The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\). 
  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
  The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
  From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
  We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
  We show that for ionized regions, the latter one, can be related to density fluctuations and use its diagnostic no determine the presence of turbulence induced-density.

@@

%In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
%In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
%Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.

@@

% In the Figs. \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
% In the Figs. the black solid line is the input regression line which is described by the equation shown in the plot and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.

@@

In this appendix we describe a simple toy model to illustrate
how fluctuations of emissivity,
combined with an ordered velocity gradient along the line of sight,
can give rise to apparent fluctuations on the plane of the sky
of the mean velocity.
The model is illustrated in the inset of Figure~\ref{fig:bright-to-vel-fluct}.
It consists of two overlapping emission layers, A and B,
with velocities along the line of sight \(v_A = 0\) and \(v_B = \beta\), respectively,
which are observed along two lines of sight (LOS), 1 and 2.
The emissivity of layer A is \(E_{A1} = E_{A2} = 1\) for both LOS,
while the emissivity of layer B is \(E_{B1} = \alpha\) for LOS~1
and \(E_{B2} = \alpha^{-1}\) for LOS~2, where \(\alpha\) is a positive constant.
Both layers are assumed to have unit depth along line line of sight,
such that the surface brightness for the two LOS are given by
\(S_1 = 1 + \alpha\) and \(S_2 = 1 + \alpha^{-1}\).

@@

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

\
Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
Using the observed structure function and by simple linear interpolation the value of \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.05}{pc} \) (as comparison to the derived values from our model which are \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \) (this \(r\) value would be analog to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
The maximum \(B(r)\) value correspond to \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\).
From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
This 'hook' behavior is described by the tapered fluctuations (see section~\ref{sec:limit-model-struct}).
If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
On their work, they only consider one Gaussian component fit.
They find tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
They also make a comparison with previous work (see table~5 on their paper) founding a a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
The work by \citet{arthur2016turbulence} is the only one that has calculated the structure function for the \ha{} emission line, for this reason it will be the only one that we use for comparison.
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] and [NII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\)..
For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see figure~2 on their paper).
Since there are the same observations there is a good agreement in the structure function.

@@

\subsubsection{Comparison with previous studies}
\label{sec:comparison-lagoon}
The Lagoon Nebula was previously studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line.
The structure function was computed on an area of \num{1} \(\times\) \SI{1}{arcmin^2} centered at Herschel 36.
Compared to our data (from \num{0.1} and \SI{10}{pc}), this covers the small scales between \num{0.012} and \SI{0.3}{pc}.
\citet{Chakraborty:1999a} findings are a power law behavior of \(m = 0.46\)
for all its range.
They mentioned the nebular gas physical conditions and the presence of gradients as responsible for the discrepancy of the theoretical 2/3 value.
No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}), but argue the possibility that the turbulent energy input is at more than one spacial scale.
With the aid of the 2D-autocorrelation function (using \(1/e\)) they found a characteristic turbulent scale of \SI{0.12}{pc}.
We found \(r_0 = \SI{1 \pm 0.1}{pc}\) for this nebula, which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}. 
In the case of the Orion Nebula we found that the velocity dispersion
of the central region was larger than that of the extended nebula
and this could be an example of a similar phenomenon,
albeit to a more extreme degree.
\citet{Chakraborty:1999a} mentioned a good agreement between \citet{1986ApJ...304..767O}  which show different HII regions structure functions slopes between \(m = 0.18 - 0.45\) and \citet{1987ApJ...317..676O} which cover an area around 9 Sgr in M8.
The first investigation in the Lagoon nebula structure function is from \citet{1970A&A.....8..486L} which claims that a value of \(m = 2/3\) satisfies their observations agreeing with the Kolmogorov Law.

@@

The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{7}{km^{297}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{13}{pc} \).
The maximum \(B(r)\) value correspond to \SI{654}{km^{2}.s^{-2}} at \(r = \SI{21}{pc}\).
From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{250}{km^{2}.s^{-2}} at \(r =  \SI{38}{pc}\) following the tapered fluctuations behavior.
The seeing (RMS) value derived for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{1.5}{\arcsecond}) and just one point of the structure function is below this value.
Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{15}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.84}, respectively, while our derived value is \num{0.85}.

@@

\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
\citet{Melnick:2021x} \(\sigma\pos\) values range from \num{11.6} to \SI{18.2}{km.s^{-1}} for a diverse type of fits (see figure~15 on their paper).
The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between spatial scales of \num{10} and \SI{100}{pc}.
The \citet{1961MNRAS.122....1F} is in broad agreement with the \citet{Melnick:2021x} results in which they consider profiles classified as singles.
Our structure function falls between the two previous results: 
From a spatial scale of \SI{5}{pc} up to \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and from \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}}.

%This is the first time turbulence is characterized in 30~Doradus using the structure function.

@@

\subsubsection{Comparison with previous studies}
\label{sec:comparison-m33}

@@

For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
Our observations cover the brightest part of the region and have smaller resolution than theirs.
As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
Due to the different observations and methodologies a direct comparison between structure functions is not possible.

>>>>

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
  In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
  We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
  We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
  The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\). 
  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
  The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
  From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
  We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
  We show that for ionized regions, the latter one, can be related to density fluctuations and use it as a diagnostic to determine the presence of turbulence-induced density fluctuations.

@@

@@

% In the Figs. \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}. In the Figs. the black solid line is the input regression line which is described by the equation shown in the plot and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.

@@

In this appendix we describe a simple toy model to illustrate
how fluctuations of emissivity,
combined with an ordered velocity gradient along the line of sight,
can give rise to apparent fluctuations on the plane of the sky
of the mean velocity.
The model is illustrated in the inset of Figure~\ref{fig:bright-to-vel-fluct}.
It consists of two overlapping emission layers, A and B,
with velocities along the line of sight \(v_A = 0\) and \(v_B = \beta\), respectively,
which are observed along two lines of sight (LOS), 1 and 2.
The emissivity of layer A is \(E_{A1} = E_{A2} = 1\) for both LOS,
while the emissivity of layer B is \(E_{B1} = \alpha\) for LOS~1
and \(E_{B2} = \alpha^{-1}\) for LOS~2, where \(\alpha\) is a positive constant.
Both layers are assumed to have unit depth along line of sight,
such that the surface brightness for the two LOS are given by
\(S_1 = 1 + \alpha\) and \(S_2 = 1 + \alpha^{-1}\).

@@

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of the Orion Nebula near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population is documented in \citet{2001ARA&A..39...99O}.

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
Using the observed structure function and by simple linear interpolation the value of \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.05}{pc} \) (as comparison to the derived values from our model which are \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \) (this \(r\) value would be analog to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
The maximum \(B(r)\) value correspond to \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\).
From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
This 'hook' behavior is described by the tapered fluctuations (see section~\ref{sec:limit-model-struct}).
If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
On their work, they only consider one Gaussian component fit.
They find tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
They also make a comparison with previous work (see table~5 on their paper) founding a a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
The work by \citet{arthur2016turbulence} is the only one that has calculated the structure function for the \ha{} emission line, for this reason it will be the only one that we use for comparison.
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] and [NII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\).
For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see figure~2 on their paper).
Since there are the same observations there is a good agreement in the structure function.

@@

\subsubsection{Comparison with previous studies}
\label{sec:comparison-lagoon}
The Lagoon Nebula was previously studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line.
The structure function was computed on an area of \num{1} \(\times\) \SI{1}{arcmin^2} centered at Herschel 36.
Compared to our which data spans between \num{0.1} and \SI{10}{pc}), their results cover smaller scales, between \num{0.012} and \SI{0.3}{pc}.
\citet{Chakraborty:1999a} report a  law behavior of \(m = 0.46\)
for all its range.
They mentioned the nebular gas physical conditions and the presence of gradients as responsible for the discrepancy of the theoretical 2/3 value.
No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}), but argue the possibility that the turbulent energy input is at more than one spacial scale.
With the aid of the 2D-autocorrelation function (using \(1/e\)) they found a characteristic turbulent scale of \SI{0.12}{pc}.
We found \(r_0 = \SI{1 \pm 0.1}{pc}\) for this nebula, which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}. 
In the case of the Orion Nebula we found that the velocity dispersion
of the central region was larger than that of the extended nebula
and this could be an example of a similar phenomenon,
albeit to a more extreme degree.
\citet{Chakraborty:1999a} mentioned a good agreement between \citet{1986ApJ...304..767O}  which show different HII regions structure functions slopes between \(m = 0.18 - 0.45\) and \citet{1987ApJ...317..676O} which cover an area around 9 Sgr in M8.
The first investigation in the Lagoon nebula structure function is from \citet{1970A&A.....8..486L} which claims that a value of \(m = 2/3\) satisfies their observations agreeing with the Kolmogorov Law.

@@

The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{297}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{13}{pc} \).
The maximum \(B(r)\) value correspond to \SI{654}{km^{2}.s^{-2}} at \(r = \SI{21}{pc}\).
From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{250}{km^{2}.s^{-2}} at \(r =  \SI{38}{pc}\) following the tapered fluctuations behavior.
The seeing (RMS) value derived for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{1.5}{\arcsecond}) and just one point of the structure function is below this value.
Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{15}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.84}, respectively, while our derived value is \num{0.85}.

@@

\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
This does not agree with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution is not completely random.
\citet{Melnick:2021x} \(\sigma\pos\) values range from \num{11.6} to \SI{18.2}{km.s^{-1}} for a diverse type of fits (see figure~15 on their paper).
The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between spatial scales of \num{10} and \SI{100}{pc}.
The \citet{1961MNRAS.122....1F} is in broad agreement with the \citet{Melnick:2021x} results in which they consider profiles classified as singles.
The large scales of our structure function falls between the two previous results.
The previous happens at \SI{5}{pc} and \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and for \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}} where our results show a downward 'hook' pattern.

@@

\subsubsection{Comparison with previous studies}
\label{sec:comparison-m33}
For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
Our observations cover the brightest part of the region and have smaller resolution than theirs.
As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
As a comparison, for the filtered turbulent parameters they chose to represent the turbulent field, the derive a total  decorrelation length (\(C(\tau_0) = 0\)) of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
Due to the different observations and methodologies a direct comparison between structure functions is not possible.

@@
